Universal Anonymous Signatures

### 2022-04-12 prism-backend/research/gsac/construction-uas.tex
Slightly refined UAS model. Working on generic construction.

\subsubsection{Commitments}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
  \item[$\Cparm \gets \CSetup(\Csecpar).$]
  \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
  \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
  \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
\end{description}

\subsubsection{Signatures with Proofs of Knowledge}

As put forward in \cite{cl02}, a generic way to build anonymous credentials
requires a digital signature scheme with efficient protocols for proving
knowledge of a digital signature, and signing committed values. This approach
also has much in common with the Sign-Randomize-Prove (SRP) approach to build
group signatures \needcite. Thus, even a priori, it seems a good core component
to build something that is actually in betwween GS and AC. In the sequel, we use
\RS to refer to schemes of this type, which must provide the functionality
specified by the following syntax:

\begin{description}
\item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
  consisting on the signig key \RSsk and the verification key \RSvk, which
  support sigining blocks of up to \RSlen messages.
\item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
  a set of messages \msgset, and a set of commitments to messages, where
  $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
\item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
  \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
  contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
    \amsgset, it is possible to know which are commitments and wich plain
    messages?}
\item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
  \RSsig, over set of messages (and commitments to messages) \amsgset, out of
  which those indexed by set \D are to be revealed, creates a proof of knowledge
  \RSproof of \RSsig.
\item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
  a signature over a set of messages, which includes \msgset, returns $1$ or
  $0$.
\end{description}

\todo{Summarise correctness and security.}

\subsubsection{Digital Signatures}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
\item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
\item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
\end{description}

\subsubsection{Encryption}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
\item[$\Ec \gets \EEnc(\Eek,\msg)$.]
\item[$\msg \gets \EDec(\Edk,\Ec)$.]
\end{description}

\subsubsection{Non-Interactive ZK Proofs of Knowledge}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
\item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
\item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
\end{description}

We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
given NP language \Lang.

\subsubsection{Signature Proofs of Knowledge}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
\item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
\end{description}

We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
given NP language \Lang.

\subsection{Generic Construction \CUASGen}

@@

\paragraph{$\parm \gets \Setup(\secpar)$.} %
\begin{itemize}
  \item Parse \secpar as $(\Csecpar,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
  \item $\Cparm \gets \CSetup(\Csecpar)$
  \item $\NIZKparm \gets \NIZKSetup(\NIZKsecpar)$
  \item Return $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\end{itemize}

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\item $(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar)$  
\item $\sig_{\fissue} \gets \RSSign(\RSsk,\fissue,\bot)$
\item $\ipk \gets (\RSvk,\fissue,\sig_{\fissue})$
\item $\isk \gets \RSsk$
\item Return $(\ipk,\isk)$
\end{itemize}

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$
\item $(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$
\item $\sig_{\finsp} \gets \SSign(\Ssk,\finsp)$
\item $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$
\item $\osk \gets (\Ssk,\Edk)$
\item Return $(\opk,\osk)$
\end{itemize}

\paragraph{$(\upk,\usk) \gets \UKeyGen(\parm)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$
\item Return $(\Svk,\Ssk)$
\end{itemize}

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
  \rangle$.} %
We define the NP language $\LangIss = \lbrace (\usk,
\ldblbrace \cred_i \rdblbrace_{i \in \Issuers}): \fissue(\usk,\attrs,\ldblbrace
(\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers}) = 1 \land \Ccom = \CCommit(\usk)
\rbrace$ \todo{\fissue needs to ensure that all {\cred}s are linked to \usk. How
  to capture this?} The interactive protocol from a user to obtain a credential
from an issuer of the system is as follows:

\begin{itemize}
\item Issuer: $\ch \gets \bin^*$; Send \ch to User.
\item User:
  \begin{itemize}    
  \item $\Ccom_{\usk} \gets \CCommit(\usk)$
  % \item $\SPKproof^{\Lang} \gets
  %   \SPK \lbrace (\usk): \Ccom_{\usk} = \CCommit(\Cparm,\usk) \rbrace (\ch)$
  \item $\SPKproof^{\LangIss} \gets \SPKProve^{\LangIss}
    (\ch,(\attrs,\Ccom_{\usk}, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers}),
    (\usk,\ldblbrace \cred_i \rdblbrace_{i \in \Issuers}))$
  \item Send $(\attrs,\Ccom_{\usk},\SPKproof^{\LangIss})$ to Issuer
  \end{itemize}
\item Issuer:
  \begin{itemize}
%  \item $1 \stackrel{?}{=} \SPKVerify(\SPKproof^{\Lang},\Ccom_{\upk})$
  \item $1 \stackrel{?}{=} \SPKVerify(\SPKproof^{\LangIss},\ch,
    (\attrs,\Ccom_{\usk}, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers}))$
  \item $\cred \gets \RSSign(\isk,\attrs,\Ccom_{\usk})$
  \item $\utrans \gets (\Ccom_{\usk},\cred,\attrs)$
  \item Send \cred to User and output \utrans.
  \end{itemize}
\item User:
  \begin{itemize}
  \item $1 \stackrel{?}{=} \RSVerify(\RSvk,\cred,(\attrs,\Ccom_{\usk}))$
  \item Output \cred
  \end{itemize}   
\end{itemize}

>>>>

\paragraph{Vector Commitment schemes.} %
Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
messages \msgset, from which we may omit randomness $r$. \todo{Informally define
  hiding and binding, leaving formal definitions to the appendix.}

\paragraph{Encryption.} %
Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
  security properties we'll need.}

\paragraph{Digital Signatures.} %
Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
verification key \Svk. \todo{Informally define security properties we'll need.}

\paragraph{Non-Interactive Zero-Knowledge.} %
We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
model \needcite. Informally, a NIZK scheme over an NP relation \NIZKRel is
defined as a tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,
\NIZKVerify^\NIZKRel)$. Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel
(\NIZKsecpar)$ produces the common reference string \NIZKcrs. $\NIZKproof/\bot
\gets \NIZKProve^\NIZKRel(\NIZKcrs,\NIZKw,\NIZKx)$ creates a NIZK proof of
knowledge of witness \NIZKw for \NIZKx such that $(\NIZKw,\NIZKx) \in \NIZKRel$.
$1/0 \gets \NIZKVerify^\NIZKRel(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof.
\todo{Informally define security properties we'll need.}

\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
We use signature schemes that allow signing messages, or commitments to messages,
in blocks, and are compatible with (efficient) proof systems over the produced
signature and signed (commitments to) messages. For this purpose, we define such
schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
verification-signing key
pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
signature over a set of committed messages \Ccom and a set of messages
\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
over message set $\overline{\msgset}$, which must contain both the messages that
were signed as commitments as well as those signed in ``the clear''. In
addition, the produced signatures must be compatible with (efficient) NIZK
proofs of knowledge of a signature, and of (arbitrary) claims over the signed
(committed) messages.
\todo{Informally define security properties we'll need.}

% \subsubsection{Commitments}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
%   \item[$\Cparm \gets \CSetup(\Csecpar).$]
%   \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
%   \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
%   \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
% \end{description}

% \subsubsection{Signatures with Proofs of Knowledge}

% As put forward in \cite{cl02}, a generic way to build anonymous credentials
% requires a digital signature scheme with efficient protocols for proving
% knowledge of a digital signature, and signing committed values. This approach
% also has much in common with the Sign-Randomize-Prove (SRP) approach to build
% group signatures \needcite. Thus, even a priori, it seems a good core component
% to build something that is actually in betwween GS and AC. In the sequel, we use
% \RS to refer to schemes of this type, which must provide the functionality
% specified by the following syntax:

% \begin{description}
% \item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
%   consisting on the signig key \RSsk and the verification key \RSvk, which
%   support sigining blocks of up to \RSlen messages.
% \item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
%   a set of messages \msgset, and a set of commitments to messages, where
%   $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
% \item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
%   \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
%   contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
%     \amsgset, it is possible to know which are commitments and wich plain
%     messages?}
% \item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
%   \RSsig, over set of messages (and commitments to messages) \amsgset, out of
%   which those indexed by set \D are to be revealed, creates a proof of knowledge
%   \RSproof of \RSsig.
% \item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
%   a signature over a set of messages, which includes \msgset, returns $1$ or
%   $0$.
% \end{description}

% \todo{Summarise correctness and security.}

% \subsubsection{Digital Signatures}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
% \item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
% \item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
% \end{description}

% \subsubsection{Encryption}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
% \item[$\Ec \gets \EEnc(\Eek,\msg)$.]
% \item[$\msg \gets \EDec(\Edk,\Ec)$.]
% \end{description}

% \subsubsection{Non-Interactive ZK Proofs of Knowledge}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
% \item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
% \item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
% \end{description}

% We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
% given NP language \Lang.

% \subsubsection{Signature Proofs of Knowledge}

% \todo{Introduce, and summarise correctness and security.}

% \begin{description}
% \item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
% \item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
% \end{description}

% We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
% given NP language \Lang.

\subsection{Generic Construction \CUASGen}
\label{ssec:generic-construction-uas}

We use three different NP relations in our generic construction. Namely,
$\NIZKRel_{\Issue}$ for issuance, $\NIZKRel_{\Sign}$ for signing, and
$\NIZKRel_{\Inspect}$ for inspection. We will be defining them in the
corresponding protocol/algorithm.

@@

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
\begin{itemize}
\item Parse \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$
\item $\Cparm \gets \CSetup(\Csecpar)$
\item $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$
\item $\Sparm \gets \SSetup(\Ssecpar)$  
\item $\Eparm \gets \ESetup(\Esecpar)$
\item $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$
\item $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$
\item $\NIZKcrs_{\Inspect} \gets \NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$
\item Return $(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
  \NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},\AttrSpace)$
\end{itemize}

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
\begin{itemize}
\item Parse \parm as $(\cdot,\SBCMparm,\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
\item $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$  
\item $\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$
\item $\ipk \gets (\Svk,\fissue,\sig_{\fissue})$
\item $\isk \gets \Ssk$
\item Return $(\ipk,\isk)$
\end{itemize}

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
\begin{itemize}
\item Parse \parm as $(\cdot,\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
\item $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$
\item $\sig_{\finsp} \gets \SSign(\Ssk,\finsp)$
\item $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$
\item $\osk \gets (\Ssk,\Edk)$
\item Return $(\opk,\osk)$
\end{itemize}

\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar,\AttrSpace)$
\item $\usk \getr \AttrSpace$
\item Return \usk
\end{itemize}

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\ldblbrace (\cred_i,\ipk_i)\rdblbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\upk,\attrs,\ldblbrace \ipk_i \rdblbrace_{i \in \Issuers},\attrs)
  \rangle$.} %
To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
issued by issuers with public keys $\ipk_i$, requests a signature on commitments
of both the user key and a new random credential identifier -- similarly to
\GSAC. In addition, the user proves that the issuance function \fissue
established by the issuer is satisfied by the $\cred_i$ credentials and its user
secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
\credid,\scred), (\Ccom,\attrs): \Ccom = \CCommit((\usk,\credid)) \land
\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred, \usk \in \cred
\rbrace$. \todo{Refine the notation for $\attr \in \cred$. Also, need to make
  the {\ipk}s explicit in it.} The interactive protocol from a user to obtain a
credential from an issuer of the system is as follows:

\begin{itemize}
\item \uline{User}: Compute a fresh credential identifier $\credid \getr
  \AttrSpace$, and commit to it along with the user secret key with
  $\Ccom \gets \CCommit((\usk,\credid))$. Compute proof $\NIZKproof \gets
  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\credid,\scred),
  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
  (\NIZKcrs_{\Issue},(\Ccom,\attrs))$, and abort if it fails. Then, compute
  the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,\attrs)$.
  Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,\NIZKproof)$.
\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
  \attrs \cup \lbrace \usk,\credid \rbrace)$. Reject if verification fails.
  Otherwise, return \cred.
\end{itemize}

### 2022-04-12 prism-backend/research/gsac/model-uas.tex
Slightly refined UAS model. Working on generic construction.

\paragraph{Helper Function \Identify.} %
\todo{We use extract now...} In addition, we make use of a helper
function \Identify for some of our definitions. This function receives
a signature and a user secret key, and determines whether the latter was used
to produce the former. This is in line with previous works on DAA
\cite{bfg+11,cdl16} and group signatures without traditional open functions
\cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
\gets \Identify(\usk,\sig)$, conveys meaning to our definitions conditioned on
the fact that, given a signature \sig accepted by \Verify, \Identify returns $1$
for exactly one \usk.

@@

>>>>

\paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
we assume the existence of two functions, \ExtractIssue and \ExtractSign. They
are not functions available in the actual scheme, but rather to the challenger,
in the experiments we use to formalize security fof \UAS. Indeed, similar
techniques have been used before to prove security in privacy-preserving schemes
with some sort of accountability, but that do not offer conventional opening as
vanilla group signatures. For instance, see related works on DAA
\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}
More concretely, both functions are as follows:

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred)$.] Receives an
$\langle \Obtain, \Issue \rangle$ transcript, and returns the credentials (if
any) and user secret key used during the execution of the protocol. It clearly
needs an honest issuer as, otherwise, the transcripts won't be available.
Consequently, we only use it to define the properties that require an honest
issuer.
\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
Receives a signature pair $(\sig,\yeval)$, as well as the inspector identifier
\oid, and the identifiers of all issuers of the credentials used to produce the
signature over \msg, and for \feval. It outputs the user secret key
and credentials used to generate the signature.
\end{description}

Note that, both for \ExtractIssue and \ExtractSign, in the case of transcripts
and signatures by honest users, it is enough to have access to the corresponding
state information (described below) maintained by the challenger in our
experiments. For join transcripts of corrupt users, or dishonestly produced
signatures, we do need to perform actual extraction. How to do this will depend
on each specific construction. Certainly, the challenger needs special
knowledge/power such as decryption trapdoors, the ability to rewind the game, or
program random oracles; the approach needs thus to depend on the concrete
construction. Although, for the case of \ExtractIssue, online extractability
(or alternative requirements, such as non-parallel or logarithmic number of
joins) is necessary. \todo{\needcite Paper from Camenisch and Shoup on the need
  for online extractability?} \todo{How do we do this in our construction(s)?
  Can we be more specific here? Also, this poses an interesting question: Is
  extraction a requirement for this kind of schemes? Can we find alternative
  definitions?}

@@

% \paragraph{Extractability.} %
% \commentwho{Jesus}{I have a doubt here. On one hand, modelling the
%   extractability-related properties here as in \cite{lnpy21} would lead to
%   redundancy with the current unforgeability properties. I do like the
%   precission in the definition of \cite{lnpy21}; but I do not like that,
%   within the extractability property, they include ``domain-specific''
%   concepts (e.g., open, etc.) On the other hand, we could model extractability
%   as (an extension of) the Identify approach in e.g. \cite{gl19,dl21}. What
%   I like about that is that it would not be redundant (we just assume the
%   existance of a function extracting some secret values). What I do not like,
%   is that the definition is not as precise as in \cite{lnpy12}. Namely, at the
%   design stage, one just has to informally describe what Identify-Extract does;
%   then, what it *really* does, has to be defined in the security proofs. That
%   is, its definition is somehow deferred, which makes the presentation a bit
%   harder to follow, IMO.}

% Before getting into the ``actual'' security properties, we introduce an
% auxiliary yet crucial property, extractability, that will allow us to formally
% define unforgeability-related properties in a meaningful way. More concretely,
% we require issuance extractability, and signing extractability. Informally, with
% issuance extractability we require that given an additional trapdoor generated
% at setup time, it is possible to extract the witnesses (user secret key and
% credentials) used to request issuance of a new credential, from its $\langle
% \Obtain,\Issue \rangle$ transcript. With signing extractability, we refer to the
% requirement to be able to extract, given an additional trapdoor, the user secret
% key and credentials used to produce any (possibly maliciously generated)
% signature. The need to differentiate both comes from the fact that, for issuance
% extractability, we need to assume honest issuers -- as otherwise, the $\langle
% \Obtain,\Issue\rangle$ transcripts may
% just not exist. Other than that, both properties are essentially the same: given
% some proof an instance of an NP relation, they allow extracting the
% corresponding witnesses. The need to resort to this extraction technique comes
% from the fact of not including a conventional opening functionality. Indeed,
% this has been used (at times, somehow implicitly) in related works on DAA
% \cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.

% In more detail, we require the existence of three additional algorithms,
% \ExtractSetup, \ExtractIssue, and \ExtractSign, as follows:

% \begin{description}
% \item[$\ExtractSetup(1^\secpar) \rightarrow (\parm,\extracttrap)$.] \todo{Describe,
%     and mention that it must be indistinguishable from \Setup.}
% \item[$\ExtractIssue(\extracttrap,\utrans) \rightarrow (\usk,\scred)$.] \todo{Describe.}
% \item[$\ExtractSign(\extracttrap,\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
%   \todo{Describe.}
% \end{description}

% With these algorithms, we formally define the issuance extractability and
% signing extractability properties as shown in \figref{fig:exp-uas-extract}.

% \begin{figure}[htp!]
%   \procedure{$\ExpExtractIssue(\utrans)$}{%
%     \pcreturn (\usk,\scred) \\    
%   }

%   \procedure{$\ExpExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
%     \pcreturn (\usk,\scred)
%   }

%   \caption{Issuance and signing extractability experiments for \UAS schemes.}
%   \label{fig:exp-uas-extract}
% \end{figure}

% \begin{definition}{(Extractable issuance of \UAS)}
%   We define the advantage \AdvExtractIssue of $\adv$ against \ExpExtractIssue as
%   $\AdvExtractIssue=\Pr\lbrack\ExpExtractIssue(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has extractable issuance if, for any p.p.t. adversary $\adv$,
%   \AdvExtractIssue is a negligible function of $1^\secpar$.
% \end{definition}

% \begin{definition}{(Extractable signing of \UAS)}
%   We define the advantage \AdvExtractSign of $\adv$ against \ExpExtractSign as
%   $\AdvExtractSign=\Pr\lbrack\ExpExtractSign(1^\secpar)=1\rbrack$.
%   %
%   A \UAS scheme has extractable signing if, for any p.p.t. adversary $\adv$,
%   \AdvExtractSign is a negligible function of $1^\secpar$.
% \end{definition}

% For short, we say that an \UAS scheme that has both extractable issuance and
% signing, is an extractable \UAS scheme.
